---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# clash

<!-- badges: start -->
<!-- badges: end -->

`clash` provides an R interface to the [Clash of Clans
API](https://developer.clashofclans.com/#/).

## Installation

You can install the development version of `clash` from
[GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("christopherkenny/clash")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(clash)
## basic example code
```


## Disclaimer

**This content is not affiliated with, endorsed, sponsored, or
specifically approved by Supercell and Supercell is not responsible for
it. For more information see Supercell’s Fan Content Policy:
\<www.supercell.com/fan-content-policy\>.**
